### 2011-09-20 doc/theses/vitasek/chapter-4-2-experiments-results.tex
Thesis: in progress.

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Input data        & \dataset{100-100}, \dataset{100-200}, \dataset{100-1000}, \dataset{OVA1}, \dataset{OVA2}, \dataset{OVA3} \\
  Iterations        & 50 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  CH                & \heu{Random} \\
  IHs               & \heu{RR} $\rightarrow$ \heu{MUT} $\rightarrow$ \heu{RR} $\rightarrow$ \heu{CX} $\rightarrow$ \heu{RW} $\rightarrow \ldots $ \\
  \hline
\end{tabular}
\bigskip
\end{center}

This experimental set will consist of 45 ratio combinations * 6 data sets * 50 iterations = 13500 experimental configurations. CH will be \heu{Random} with pool size of 10. IHs will be the ones from Scenario 1, with their ratios set to one of the 45 combinations produced in the following way.
\begin{itemize}
	\item \heu{RandomRemove} ratio will be from $\{0, 0.05, 0.1, 0.2, 0.5\}$
	\item \heu{Mutatio} ratio will be from $\{0.05, 0.1, 0.2\}$
	\item \heu{Crossover} ratio will be from $\{0.05, 0.1, 0.2\}$
\end{itemize}
The process of creating the configurations is captured in Listing \ref{listing-experiment-chained-ihs-tuning}. We will be gathering the following information for each run: what were the parameters, how long did the run take and whether it found optimum.\\

@@

\FOR{$rrRatio \in \{0, 0.05, 0.1, 0.2, 0.5\}$}
\FOR{$mutRatio \in \{0.05, 0.1, 0.2\}$}
\FOR{$cxRatio \in \{0.05, 0.1, 0.2\}$}
  \STATE $RR \gets \heu{RandomRemoval}(ratio = rrRatio)$
  \STATE $MUT \gets \heu{Mutation}(ratio = mutRatio, limit = 1)$
  \STATE $CX \gets \heu{Crossover}(ratio = cxRatio, limit = 1)$
  \FOR{$file \in \{\dataset{100-100}, \dataset{100-200}, \dataset{100-1000}, \dataset{OVA1}, \dataset{OVA2}, \dataset{OVA3}\}$}
    \FOR{$i = 1 \to 50$}
      \STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = (\heu{RR}, \heu{MUT}, \heu{RR}, \heu{CX}, \heu{RW})\}$
    \ENDFOR
  \ENDFOR
\ENDFOR
\ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

@@

>>>>

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Input data        & all sized test data sets \\
  Iterations        & 25 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  CH                & \heu{Random} \\
  IHs               & \heu{RR} $\rightarrow$ \heu{MUT} $\rightarrow$ \heu{RR} $\rightarrow$ \heu{CX} $\rightarrow$ \heu{RW} $\rightarrow \ldots $ \\
  \hline
\end{tabular}
\bigskip
\end{center}

This experimental set will consist of 45 ratio combinations * 11 data sets * 25 iterations = 12375 experimental configurations. CH will be \heu{Random} with pool size of 10. IHs will be the ones from Scenario 1, with their ratios set to one of the 45 combinations produced in the following way.
\begin{itemize}
	\item \heu{RandomRemove} ratio will be from $\{0, 0.05, 0.1, 0.2, 0.5\}$
	\item \heu{Mutatio} ratio will be from $\{0.05, 0.1, 0.2\}$
	\item \heu{Crossover} ratio will be from $\{0.05, 0.1, 0.2\}$
\end{itemize}
The process of creating the configurations is captured in Listing \ref{listing-experiment-chained-ihs-tuning}. We will be gathering the following information for each run: what were the parameters, how long did the run take and whether it found optimum.\\

@@

\FOR{$rrRatio \in \{0, 0.05, 0.1, 0.2, 0.5\}$}
\FOR{$mutRatio \in \{0.05, 0.1, 0.2\}$}
\FOR{$cxRatio \in \{0.05, 0.1, 0.2\}$}
  \STATE $RR \gets \heu{RandomRemoval}(ratio = rrRatio)$
  \STATE $MUT \gets \heu{Mutation}(ratio = mutRatio, limit = 1)$
  \STATE $CX \gets \heu{Crossover}(ratio = cxRatio, limit = 1)$
  \FOR{$file \in $ sized test data}
    \FOR{$i = 1 \to 50$}
      \STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = (\heu{RR}, \heu{MUT}, \heu{RR}, \heu{CX}, \heu{RW})\}$
    \ENDFOR
  \ENDFOR
\ENDFOR
\ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

% TODO we ignore the time, instead we use the ratio of successful runs

@@

% TODO replace this table

@@

% TODO the ratios actually are 0.5, 0.2 and 0.1, consistently across all all data sets
